Appendix of Bauer et al. (2023) Dike experiment

### 2023-02-28 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

```{r table-flood-weather, tab.id = "flood-weather", tab.cap = ""}
read_csv(here::here("data", "raw", "data_raw_table_a1.csv")) %>%
  flextable() %>%
  bold(part = "header") %>%
  compose(part = "body", i = ~ Unit == "m3 s−1", j = "Unit", value = as_paragraph("m", as_sup("3"), " s", as_sup("−1"))) %>%
  autofit()
```

@@

```{r tab.id = "establishment", tab.cap = ""}
read_csv(
  here("data", "processed", "data_processed_traits.csv"),
  col_names = TRUE,
  na = c("na", "NA"),
  col_types = cols(.default = "?", name = "f")
  ) %>%
  select(name, family, total_seeded_2018, starts_with("rate_")) %>%
  drop_na(total_seeded_2018) %>%
  arrange(match(family, c("Poaceae", "Fabaceae"))) %>%
  mutate(
    across(starts_with("rate"), ~ .x * 100),
    name = str_replace_all(name, "_", " ")) %>%
  rename(
    Species = name,
    Family = family,
    "Seeded plots [#]" = total_seeded_2018,
    "Establishment rate [%]" = rate_2018,
    "2019" = rate_2019,
    "2020" = rate_2020,
    "2021" = rate_2021
    ) %>%
  flextable() %>%
  align(part = "all", align = "center", j = -1) %>%
  merge_at(part = "header", j = 4:7) %>%
  add_header_row(top = FALSE, values = c("", "", "", "2018", "2019", "2020", "2021")) %>%
  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
  bold(part = "header") %>%
  style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
  bg(j = 4:7, bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 100))) %>%
  autofit()
```

@@

```{r tab.id = "specieslist", tab.cap = ""}
read_csv(
  here("outputs", "tables", "table_a5_specieslist.csv"),
  col_names = TRUE,
  na = c("na", "NA"),
  col_types = cols(.default = "?", name = "f")
  ) %>%
  mutate(name = str_replace_all(name, "_", " ")) %>%
  rename(
    Name = name,
    Seeded = seeded,
    "Target species" = target,
    "Presence [# plots]" = sum
    ) %>%
  flextable() %>%
  align(part = "all", align = "center", j = -1) %>%
  bold(part = "header") %>%
  style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
  bg(j = 4, bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 931))) %>%
  autofit()
```

>>>>

```{r table-flood-weather, tab.id = "flood-weather", tab.cap = ""}
read_csv(here::here("data", "raw", "data_raw_table_a1.csv")) %>%
  flextable() %>%
  bold(part = "header") %>%
  compose(
    part = "body",
    i = ~ Unit == "m3 s−1",
    j = "Unit",
    value = as_paragraph("m", as_sup("3"), " s", as_sup("−1"))
    ) %>%
  autofit()
```

@@

```{r tab.id = "establishment", tab.cap = ""}
read_csv(
  here("data", "processed", "data_processed_traits.csv"),
  col_names = TRUE,
  na = c("na", "NA"),
  col_types = cols(.default = "?", name = "f")
  ) %>%
  select(name, family, total_seeded_2018, starts_with("rate_")) %>%
  drop_na(total_seeded_2018) %>%
  arrange(match(family, c("Poaceae", "Fabaceae"))) %>%
  mutate(
    across(starts_with("rate"), ~ .x * 100),
    name = str_replace_all(name, "_", " ")) %>%
  rename(
    Species = name,
    Family = family,
    "Seeded plots [#]" = total_seeded_2018,
    "Establishment rate [%]" = rate_2018,
    "2019" = rate_2019,
    "2020" = rate_2020,
    "2021" = rate_2021
    ) %>%
  flextable() %>%
  align(part = "all", align = "center", j = -1) %>%
  merge_at(part = "header", j = 4:7) %>%
  add_header_row(
    top = FALSE,
    values = c("", "", "", "2018", "2019", "2020", "2021")
    ) %>%
  border_inner_h(part = "header", border = fp_border(width = 1)) %>%
  bold(part = "header") %>%
  style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
  bg(
    j = 4:7,
    bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 100))
    ) %>%
  autofit()
```

@@

```{r tab.id = "specieslist", tab.cap = ""}
read_csv(
  here("outputs", "tables", "table_a5_specieslist.csv"),
  col_names = TRUE,
  na = c("na", "NA"),
  col_types = cols(.default = "?", name = "f")
  ) %>%
  mutate(name = str_replace_all(name, "_", " ")) %>%
  rename(
    Name = name,
    Seeded = seeded,
    "Target species" = target,
    "Presence [# plots]" = sum
    ) %>%
  flextable() %>%
  align(part = "all", align = "center", j = -1) %>%
  bold(part = "header") %>%
  style(j = 1, pr_t = fp_text_default(italic = TRUE)) %>%
  bg(
    j = 4,
    bg = scales::col_numeric(palette = c("white", "grey60"), domain = c(0, 931))
    ) %>%
  autofit()
```
